
# Temperature prediction

- Date - Present day: yyyy-mm-dd ('2013-06-30' to '2017-08-30')
- Present_Tmax - Maximum air temperature (0 and 21 h) on the present day (Â°C): 20 to 37.6
- Present_Tmin - Minimum air temperature between 0 and 21 h on the present day (Â°C): 11.3 to 29.9
- LDAPS_RHmin - LDAPS model forecast of next-day minimum relative humidity (%): 19.8 to 98.5
- LDAPS_RHmax - LDAPS model forecast of next-day maximum relative humidity (%): 58.9 to 100
- LDAPS_Tmax_lapse - LDAPS model forecast of next-day maximum air temperature applied lapse rate (Â°C): 17.6 to 38.5
- LDAPS_Tmin_lapse - LDAPS model forecast of next-day minimum air temperature applied lapse rate (Â°C): 14.3 to 29.6
- LDAPS_WS - LDAPS model forecast of next-day average wind speed (m/s): 2.9 to 21.9
- LDAPS_LH - LDAPS model forecast of next-day average latent heat flux (W/m2): -13.6 to 213.4
- LDAPS_CC1 - LDAPS model forecast of next-day 1st 6-hour split average cloud cover (0-5 h) (%): 0 to 0.97
- LDAPS_CC2 - LDAPS model forecast of next-day 2nd 6-hour split average cloud cover (6-11 h) (%): 0 to 0.97
- LDAPS_CC3 - LDAPS model forecast of next-day 3rd 6-hour split average cloud cover (12-17 h) (%): 0 to 0.98
- LDAPS_CC4 - LDAPS model forecast of next-day 4th 6-hour split average cloud cover (18-23 h) (%): 0 to 0.97
- LDAPS_PPT1 - LDAPS model forecast of next-day 1st 6-hour split average precipitation (0-5 h) (%): 0 to 23.7
- LDAPS_PPT2 - LDAPS model forecast of next-day 2nd 6-hour split average precipitation (6-11 h) (%): 0 to 21.6
- LDAPS_PPT3 - LDAPS model forecast of next-day 3rd 6-hour split average precipitation (12-17 h) (%): 0 to 15.8
- LDAPS_PPT4 - LDAPS model forecast of next-day 4th 6-hour split average precipitation (18-23 h) (%): 0 to 16.7
- lat - Latitude (Â°): 37.456 to 37.645
- lon - Longitude (Â°): 126.826 to 127.135
- DEM - Elevation (m): 12.4 to 212.3
- Slope - Slope (Â°): 0.1 to 5.2
- Solar radiation - Daily incoming solar radiation (wh/m2): 4329.5 to 5992.9
- Next_Tmax - The next-day maximum air temperature (Â°C): 17.4 to 38.9
- Next_Tmin - The next-day minimum air temperature (Â°C): 11.3 to 29.8

# Paquetes

```{r, message=FALSE}
library(tidymodels)
```


```{r}
temperature <- read.csv("~/Dropbox/Mi Mac (Rebeca’s MacBook Air)/Documents/ITAM.20/DecimoSemestre/Estadistica-Aplicada-I/Proyecto_Final/Data/Bias_correction_ucl.csv")

temperature
```
```{r}
temperature=temperature[complete.cases(temperature),]
```
```{r}
temperature
```
#c r e a t e dummy v a r i a b l e s f o r days and month
```{r}
library('recipes')

# Making dummy variables
dummies <- forestfires %>% recipe(area ~ .) %>%
  step_dummy(month,day,
             one_hot = TRUE)  %>% 
  prep() %>% 
  bake(forestfires)
```

```{r}
pairs(temperature[,c(12,13,14,24)])

```
```{r}
library(ISLR)
data("Portafolio")
summary(Portfolio)
attach(Portfolio)
plot(X,Y)
```

