
# Temperature prediction

- Date - Present day: yyyy-mm-dd ('2013-06-30' to '2017-08-30')
- Present_Tmax - Maximum air temperature (0 and 21 h) on the present day (Â°C): 20 to 37.6
- Present_Tmin - Minimum air temperature between 0 and 21 h on the present day (Â°C): 11.3 to 29.9
- LDAPS_RHmin - LDAPS model forecast of next-day minimum relative humidity (%): 19.8 to 98.5
- LDAPS_RHmax - LDAPS model forecast of next-day maximum relative humidity (%): 58.9 to 100
- LDAPS_Tmax_lapse - LDAPS model forecast of next-day maximum air temperature applied lapse rate (Â°C): 17.6 to 38.5
- LDAPS_Tmin_lapse - LDAPS model forecast of next-day minimum air temperature applied lapse rate (Â°C): 14.3 to 29.6
- LDAPS_WS - LDAPS model forecast of next-day average wind speed (m/s): 2.9 to 21.9
- LDAPS_LH - LDAPS model forecast of next-day average latent heat flux (W/m2): -13.6 to 213.4
- LDAPS_CC1 - LDAPS model forecast of next-day 1st 6-hour split average cloud cover (0-5 h) (%): 0 to 0.97
- LDAPS_CC2 - LDAPS model forecast of next-day 2nd 6-hour split average cloud cover (6-11 h) (%): 0 to 0.97
- LDAPS_CC3 - LDAPS model forecast of next-day 3rd 6-hour split average cloud cover (12-17 h) (%): 0 to 0.98
- LDAPS_CC4 - LDAPS model forecast of next-day 4th 6-hour split average cloud cover (18-23 h) (%): 0 to 0.97
- LDAPS_PPT1 - LDAPS model forecast of next-day 1st 6-hour split average precipitation (0-5 h) (%): 0 to 23.7
- LDAPS_PPT2 - LDAPS model forecast of next-day 2nd 6-hour split average precipitation (6-11 h) (%): 0 to 21.6
- LDAPS_PPT3 - LDAPS model forecast of next-day 3rd 6-hour split average precipitation (12-17 h) (%): 0 to 15.8
- LDAPS_PPT4 - LDAPS model forecast of next-day 4th 6-hour split average precipitation (18-23 h) (%): 0 to 16.7
- lat - Latitude (Â°): 37.456 to 37.645
- lon - Longitude (Â°): 126.826 to 127.135
- DEM - Elevation (m): 12.4 to 212.3
- Slope - Slope (Â°): 0.1 to 5.2
- Solar radiation - Daily incoming solar radiation (wh/m2): 4329.5 to 5992.9
- Next_Tmax - The next-day maximum air temperature (Â°C): 17.4 to 38.9
- Next_Tmin - The next-day minimum air temperature (Â°C): 11.3 to 29.8

# Paquetes

```{r, message=FALSE}
library(tidymodels)
```


```{r}
temperature <- read.csv("/Users/rebecaangulorojas/Dropbox/Mi Mac (Rebeca’s MacBook Air)/Documents/ITAM.20/DecimoSemestre/Estadistica-Aplicada-I/Proyecto_Final/Temperature-prediction-MultipleRegression/Data/Bias_correction_ucl.csv")

columnas = names(temperature)
# falta documentar esto
# nos quedamos con variable no nulas
columnas
````


```{r}
temperature=temperature[complete.cases(temperature),]


```

```{r}
columnas
```


```{r}
temperature <- temperature[,-c(1,2)]
#
```


```{r}
library(ggplot2)
```


# scatter plot
```{r}
ggplot(temperature, aes(x=Present_Tmax, y=Next_Tmax)) +
  geom_point(size=2, shape=23, fill = "#ff6781", colour ="#ff1f46" )
```

```{r}
# Basic scatter plot
ggplot(temperature, aes(x=Present_Tmin, y=Next_Tmax)) +
  geom_point(size=2, shape=23, fill = "#ff6781")
```
```{r}
ggplot(temperature, aes(x=LDAPS_RHmin, y=Next_Tmax)) +
  geom_point(size=2, shape=23, fill = "#ff6781")
```
```{r}
ggplot(temperature, aes(x=LDAPS_RHmin, y=Next_Tmax)) +
  geom_point(size=2, shape=23, fill = "#ff6781")
```









